Experiment 4

### 2021-07-15 experiments/experiment 4/experiment 4.Rmd
add experiment 4 (factorial)

---
title: "Experiment 1"
author: "Owen Petchey"
date: "6/25/2021"
output:
  html_document:
    keep_md: yes
---

@@

```{r}
var_expt <- create_diversity()
```

@@

@@

```{r}
default_sim_duration <- 80000
```

```{r}
sim_number <- 1
default_log10a_series <- c(-1, -7, -7)
initial_state <- new_initial_state(num_CB_strains,
                                   num_PB_strains,
                                   num_SB_strains,
                                   values = "bush_ssfig3")
initial_state[grep("CB_", names(initial_state))] <- 10^10/num_CB_strains
sim_res_novar <- run_simulation(parameter_values = var_expt$pars[[sim_number]],
                          initial_state = initial_state)
plot_dynamics(sim_res_novar)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

@@

```{r}
sim_number <- num_div_treatment_levels
sim_res_highvar <- run_simulation(parameter_values = var_expt$pars[[sim_number]],
                          initial_state = initial_state)
plot_dynamics(sim_res_highvar)
#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)

@@

```{r}
default_sim_duration <- 60000
```

```{r}
sim_number <- 1
default_log10a_series <- c(-5, -3, -1, -1)
initial_state <- new_initial_state(num_CB_strains,
                                   num_PB_strains,
                                   num_SB_strains,
                                   values = "bush_ssfig3")
initial_state[grep("CB_", names(initial_state))] <- 10/num_CB_strains
sim_res_novar <- run_simulation(parameter_values = var_expt$pars[[sim_number]],
                          initial_state = initial_state)
plot_dynamics(sim_res_novar)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

@@

```{r}
default_sim_duration <- 1000000
```

```{r}
default_minimum_abundances <- rep(100, 3)
names(default_minimum_abundances) <- c("CB", "PB", "SB")
```

```{r}
sim_number1 <- 1
default_log10a_series <- c(-1, -8, -1)
initial_state <- new_initial_state(num_CB_strains,
                                   num_PB_strains,
                                   num_SB_strains,
                                   values = "bush_ssfig3")
initial_state[grep("CB_", names(initial_state))] <- 10/num_CB_strains
sim_res_novar <- run_simulation(parameter_values = var_expt$pars[[sim_number1]],
                          initial_state = initial_state)
plot_dynamics(sim_res_novar)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

@@

```{r}
sim_number2 <- num_div_treatment_levels
sim_res_highvar <- run_simulation(parameter_values = var_expt$pars[[sim_number2]],
                          initial_state = initial_state)
plot_dynamics(sim_res_highvar)
#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)

@@

```{r}
visualise_temporal_env_eco()
```

@@

```{r}
options(mc.cores = 6)
```

```{r}
ssfind_minimum_abundances <- rep(0, 3)
names(ssfind_minimum_abundances) <- c("CB", "PB", "SB")
ssfind_simulation_duration <- default_sim_duration
ssfind_simulation_sampling_interval <- ssfind_simulation_duration
ssfind_event_interval <- ssfind_simulation_duration
grid_num_a <- 1000 ## number of a_0 values
a_Os <- 10^seq(-7, -1, length=grid_num_a) ## sequence of a_0 values
grid_num_N <- 2 ## number of N values
initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
initial_PBs <- 1e8 ## not varied
initial_SBs <- 1e8 ## not varied
# next line creates all possible combinations
ss_expt <- expand.grid(N_CB = initial_CBs,
                      N_PB = initial_PBs,
                      N_SB = initial_SBs,
                      a_O = a_Os)

@@

```{r}
var_expt <- run_ss_var_experiment()
saveRDS(var_expt, here("experiments/experiment 1/data/ss_data.RDS"))

@@

```{r}
var_expt <- readRDS(here("experiments/experiment 1/data/ss_data.RDS"))

@@

ss_result1 <- var_expt[result_index1,]$ss_res[[1]]
ss_result2 <- var_expt[result_index2,]$ss_res[[1]]
xlims = c(-7, -1)
```

```{r finalise}

>>>>

---
title: "Experiment 4"
author: "Owen Petchey"
date: "6/25/2021"
output:
  html_document:
    keep_md: yes
---

@@

```{r}
var_expt <- create_diversity_factorial()
```

@@

```{r}
eval_dynamics_flag <- FALSE
```

@@

```{r eval = eval_dynamics_flag}
default_sim_duration <- 80000
```

```{r eval = eval_dynamics_flag}
sim_number <- 1
default_log10a_series <- c(-1, -7, -7)
initial_state <- new_initial_state(num_CB_strains,
                                   num_PB_strains,
                                   num_SB_strains,
                                   values = "bush_ssfig3")
initial_state[grep("CB_", names(initial_state))] <- 10^10/num_CB_strains
sim_res_novar <- run_simulation(parameter_values = var_expt$pars[[sim_number]],
                          initial_state = initial_state)
plot_dynamics(sim_res_novar)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

@@

```{r eval = eval_dynamics_flag}
sim_number <- num_div_treatment_levels
sim_res_highvar <- run_simulation(parameter_values = var_expt$pars[[sim_number]],
                          initial_state = initial_state)
plot_dynamics(sim_res_highvar)
#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)

@@

```{r eval = eval_dynamics_flag}
default_sim_duration <- 60000
```

```{r eval = eval_dynamics_flag}
sim_number <- 1
default_log10a_series <- c(-5, -3, -1, -1)
initial_state <- new_initial_state(num_CB_strains,
                                   num_PB_strains,
                                   num_SB_strains,
                                   values = "bush_ssfig3")
initial_state[grep("CB_", names(initial_state))] <- 10/num_CB_strains
sim_res_novar <- run_simulation(parameter_values = var_expt$pars[[sim_number]],
                          initial_state = initial_state)
plot_dynamics(sim_res_novar)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

@@

```{r eval = eval_dynamics_flag}
default_sim_duration <- 1000000
```

```{r eval = eval_dynamics_flag}
default_minimum_abundances <- rep(100, 3)
names(default_minimum_abundances) <- c("CB", "PB", "SB")
```

```{r eval = eval_dynamics_flag}
sim_number1 <- 1
default_log10a_series <- c(-1, -8, -1)
initial_state <- new_initial_state(num_CB_strains,
                                   num_PB_strains,
                                   num_SB_strains,
                                   values = "bush_ssfig3")
initial_state[grep("CB_", names(initial_state))] <- 10/num_CB_strains
sim_res_novar <- run_simulation(parameter_values = var_expt$pars[[sim_number1]],
                          initial_state = initial_state)
plot_dynamics(sim_res_novar)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

@@

```{r eval = eval_dynamics_flag}
sim_number2 <- num_div_treatment_levels
sim_res_highvar <- run_simulation(parameter_values = var_expt$pars[[sim_number2]],
                          initial_state = initial_state)
plot_dynamics(sim_res_highvar)
#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)

@@

```{r eval = eval_dynamics_flag}
visualise_temporal_env_eco()
```

@@

```{r}
options(mc.cores = 12)
```

```{r}
ssfind_minimum_abundances <- rep(0, 3)
names(ssfind_minimum_abundances) <- c("CB", "PB", "SB")
ssfind_simulation_duration <- default_sim_duration
ssfind_simulation_sampling_interval <- ssfind_simulation_duration
ssfind_event_interval <- ssfind_simulation_duration
grid_num_a <- 1000 #usually 1000 ## number of a_0 values
a_Os <- 10^seq(-7, -1, length=grid_num_a) ## sequence of a_0 values
grid_num_N <- 2 ## number of N values
initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
initial_PBs <- 1e8 ## not varied
initial_SBs <- 1e8 ## not varied
# next line creates all possible combinations
ss_expt <- expand.grid(N_CB = initial_CBs,
                      N_PB = initial_PBs,
                      N_SB = initial_SBs,
                      a_O = a_Os)

@@

```{r}
var_expt <- run_ss_var_experiment()
saveRDS(var_expt, here("experiments/experiment 4/data/ss_data.RDS"))

@@

```{r}
var_expt <- readRDS(here("experiments/experiment 4/data/ss_data.RDS"))

@@

```{r}
stab_data <- var_expt %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
stab_data <- unnest(stab_data, cols = c(stability_measures))
